Software Citation Principles

### 2016-03-31 sc-principles/software-citation-principles.tex
small change to reflect section reordering a few weeks ago

Wilson suggests that software authors include a \texttt{CITATION} file that documents exactly how the authors of the software would like to be cited by others~\cite{ssi-citation-files}. While this is not a formal metadata specification (e.g., it is not machine readable) this does offer a solution for authors wishing to give explicit instructions to potential citing authors and as noted in the introduction (\S\ref{sec:intro}), there is evidence that authors follow instructions if they exist~\cite{10.1371/journal.pone.0136631}.

>>>>

Wilson suggests that software authors include a \texttt{CITATION} file that documents exactly how the authors of the software would like to be cited by others~\cite{ssi-citation-files}. While this is not a formal metadata specification (e.g., it is not machine readable) this does offer a solution for authors wishing to give explicit instructions to potential citing authors and as noted in the motivation section (\S\ref{sec:intro}), there is evidence that authors follow instructions if they exist~\cite{10.1371/journal.pone.0136631}.
